---
title: "DS-take home challenge"
author: "Chelsey"
date: "8/11/2020"
output: html_document
---

```{r}
#set working directory
setwd("D:/Projects")
working_dir <- getwd()

#create a directroy for your saved graph
data_dir <- file.path(working_dir, "data_ds_takehome_cvr")
dir.create(data_dir)

#load data
conversion_data <- read.csv(file.path("data_ds_takehome_cvr", "conversion_project.csv"))

```

```{r}

#load packages

library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(corrplot)

```

## Check the characteristics of the user in the first rows.

```{r}

head(conversion_data)
str(conversion_data)


# distribution of age
ggplot(data = conversion_data, aes(x = age)) +
  geom_histogram(stat = "count")

# check whether there is outlier
filter(conversion_data, conversion_data$age >= 80)

# remove whose age >= 80

eliminated_data <- subset(conversion_data, conversion_data$age < 80)

# transform new_user and converted

eliminated_data$new_user <- as.factor(eliminated_data$new_user)

```

## Exploratory Data Ananlysis

```{r}

#visualize the conversion among different countries

ggplot(eliminated_data, aes(x = country)) +
   geom_bar() +
   facet_wrap(~ converted)

data_country = eliminated_data %>% group_by(country) %>% summarise(conversion_rate = mean(converted))

ggplot(data = data_country, aes(x = country, y = conversion_rate)) +
   geom_bar(stat = "identity", aes(fill = country))

# visualize the conversion among user_type

ggplot(eliminated_data, aes(x = new_user)) +
   geom_bar() +
   facet_wrap(~ converted)

data_user_type = eliminated_data %>% group_by(new_user) %>% summarise(conversion_rate = mean(converted))

ggplot(data = data_user_type, aes(x = new_user, y = conversion_rate)) +
   geom_bar(stat = "identity", aes(fill = new_user))

# visualize the conversion among different source

ggplot(eliminated_data, aes(x = source)) +
   geom_bar() +
   facet_wrap(~ converted)

data_source = eliminated_data %>% group_by(source) %>% summarise(conversion_rate = mean(converted))

ggplot(data = data_source, aes(x = source, y = conversion_rate)) +
   geom_bar(stat = "identity", aes(fill = source))

#visualize converted among age

ggplot(eliminated_data, aes(x = age)) +
   geom_histogram() +
   facet_wrap(~ converted)

data_age = eliminated_data %>% group_by(age) %>% summarise(conversion_rate = mean(converted))

ggplot(data = data_age, aes(x = age, y = conversion_rate)) +
   geom_line()

#visualize converted among page_view

ggplot(eliminated_data, aes(x = total_pages_visited)) +
   geom_histogram() +
   facet_wrap(~ converted)

data_pageview = eliminated_data %>% group_by(total_pages_visited) %>% summarise(conversion_rate = mean(converted))

ggplot(data = data_pageview, aes(x = total_pages_visited, y = conversion_rate)) +
   geom_line()

```

## Machine Learning

```{r}

# divide the dataset in training and test data. 

set.seed(857262)

eliminated_data$isTrain <- rbinom(nrow(eliminated_data), 1, 0.66)
train <- subset(eliminated_data, eliminated_data$isTrain == 1)
test <- subset(eliminated_data, eliminated_data$isTrain == 0)

# generate glm model by using train data

logitmodel <- glm(converted ~ age + new_user + total_pages_visited + country + source, data = train, family = binomial )

summary(logitmodel)

#set threshold value

T = 0.3
test.prob <- predict(logitmodel, test, type = "response")
test.predict <- ifelse(test.prob >= T, 1, 0)
conversionRate <- mean(test.predict)


#compare to the "real" test data 
d_binomial_test_new <- tibble("target" = test$converted, "prediction" = test.predict)
basic_table_test_new <- table(d_binomial_test_new)
accuracyNew_test <- sum(diag(basic_table_test_new))/sum(basic_table_test_new)

accuracyNew_test

#accuracy = 98.6%, the model - logitmodel works well
#we may use this logitmodel to predict conversion rate

```

## Insight

1) Younger people are more likely to convert - we may use marketing channel userd by younger generation

2) Old users are more likely to convert
targeted emails with offers and promotions to bring existing users back

3) Germans are more likely to convert, but the user base in germany is relatively small, we may put more effort in germany market.

4) The conversion rate in china are off, there might be something wrong with the site. 
